Dismal Code: Studying the Evolution of Security Bugs

### 2013-09-16 docs/evol.tex
added percentages for the security bugs separetely

Our first results involve the most popular bugs in the Maven repository.
Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
repository. Together with the {\it Bad Practice} bugs and the {\it Style} bugs,
security bugs (the sum of the {\it Security} and {\it Malicious Code}
categories) are the most popular in the repository ($\geq 21\%$ each).
This could be a strong indication that programmers write code
that implements the required functionality without considering its many
security aspects; an issue that has already been reported in
literature~\cite{SH09}.
% An interesting observation is that 4,908 projects did not
% have any bugs at all. These cases involved small artifacts with a minimum number of classes.
% This goes along with the relationship between the size of an artifact and it's
% bugs that is presented in the upcoming section.

@@

We analysed more than 260GB of interdependent project versions to see
how security bugs evolve over time, their persistence, their relation
with other bug categories, and their relationship with size in terms
of bytecode.

@@

Our data and code will be publicly available upon publication.

>>>>

Our first results involve the most popular bugs in the Maven repository.
Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
repository. Together with the {\it Bad Practice} bugs and the {\it Style} bugs,
security bugs (the sum of the {\it Security} and {\it Malicious Code}
categories - 0.21\% + 21.81\%) are the most popular in the repository ($\geq 21\%$ each).
This could be a strong indication that programmers write code
that implements the required functionality without considering its many
security aspects; an issue that has already been reported in
literature~\cite{SH09}.
% An interesting observation is that 4,908 projects did not
% have any bugs at all. These cases involved small artifacts with a minimum number of classes.
% This goes along with the relationship between the size of an artifact and it's
% bugs that is presented in the upcoming section.

@@

We analysed more than 260GB of interdependent project versions to see
how security bugs evolve over time, their persistence, their relation
with other bug categories, and their relationship with size in terms
of bytecode.\footnote{Our data and code are available online at:
\url{https://github.com/bkarak/evol_security_publication_2012}}

@@
